---
title: "Update Trending Topics"
author: "Charliemarketplace"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
# libraries & functions here 
source("source_funcs_and_secrets.R")
```


# What this does

On a schedule:

 1. Pulls `target_twitter_accounts` and calls `pull_account_tweets`.
 2. Dump dataframe form in `raw_tweet_dump`, call `add_new_tweets()` proc to clean & append to `processed_tweets`.
 3. Ingest unused tweets to call `chatgpt_id_topic` at the day-ecosystem level and get the `subjects` and `summaries`. 
 4. Update used tweets to `used_in_summary = TRUE` and insert into `ai_summary`.
 
 Website (in-dev) offers a UI over the summaries that uses term frequency to link back to 
 relevant tweets at the day-ecosystem level.

# Pull Tweets

START: `r Sys.time()`

```{r, warning=FALSE, message=FALSE}


  target_accounts <- submitSnowflake(
    query = "select * from datascience_dev.trending_topics.target_twitter_accounts",
    creds = snowflake_credentials
    )
  
  
  # pulls latest 100 tweets for simplicity
  pull_list <- lapply(1:nrow(target_accounts), function(x){
    pull_account_tweets(account = target_accounts$USERNAME[x], 
                        id = target_accounts$TWITTER_ID[x],
                        twitter_secret = twitter_secret,
                        n = 100)
    
  })
  
  df <- do.call(rbind, pull_list)
  
  # prepare in case of single quote to escape them
  df$tweet_text <- gsub("'", "''", df$tweet_text)
  
  values <- apply(df, 1, function(row) {
    sprintf("('%s', '%s', '%s', '%s')",
            row['created_at'], row['username'], row['tweet_text'], row['twitter_id'])
  })
  
  insert_query <- sprintf(
    "INSERT INTO datascience_dev.trending_topics.raw_tweet_dump (created_at, username, tweet_text, tweet_id) VALUES %s",
    paste(values, collapse = ",")
  )
  
  submitSnowflake(insert_query, creds = snowflake_credentials)
  
  res_ <- submitSnowflake("call datascience_dev.trending_topics.add_new_tweets()", creds = snowflake_credentials)
  
```

INGEST: `r Sys.time()`

# Summarize 

```{r, message=FALSE, warning=FALSE}

unused_ <- submitSnowflake(query = {
    " 
    select 
    t.CREATED_AT, t.DAY_, t.USERNAME,
    t.TWEET_TEXT, t.TWEET_ID, 
    t.USED_IN_SUMMARY, 
    a.ECOSYSTEM
    from 
    datascience_dev.trending_topics.processed_tweets t left join datascience_dev.trending_topics.target_twitter_accounts a 
    USING (USERNAME)
    where used_in_summary = FALSE
    "
  }, creds = snowflake_credentials)
  
  # for each ecosystem, each day - get a summary of tweets across accounts 
  
  unique_eco_days <- unique(unused_[, c("DAY_","ECOSYSTEM")] )
  
  for(i in 1:nrow(unique_eco_days)){
    
    temp_day <- unique_eco_days$DAY_[i]
    temp_ecosystem <- unique_eco_days$ECOSYSTEM[i]
    
    temp_tweets <- unused_[
      unused_$DAY_ == temp_day & 
      unused_$ECOSYSTEM == temp_ecosystem, ]
    
    temp_ids_used <- temp_tweets$TWEET_ID
    
    tweet_text <- paste0(temp_tweets$TWEET_TEXT, collapse = " %%% ")
    chat_topics <- chatgpt_id_topic(tweet_text, chatgpt_secret, prompt)
    subjects <- get_subject(chat_topics)
    subjects <- subjects[nchar(subjects)  > 0]
    summaries <- get_summaries(chat_topics)
    summaries <- summaries[nchar(summaries)  > 0]
    
    # update the IDs used as used
    
    update_query <- sprintf(
      "UPDATE datascience_dev.trending_topics.processed_tweets 
       SET used_in_summary = TRUE 
       WHERE tweet_id IN (%s)",
      paste0("'", temp_ids_used, "'", collapse = ",")
    )
    
    submitSnowflake(update_query, creds = snowflake_credentials)
    
    # insert the ai summaries into their table 
    
    current_date <- format(Sys.Date(), "%Y%m%d")
    summary_id <- paste(temp_day, temp_ecosystem, current_date, sep = "_")
    
    # Escape single quotes in text fields
    subjects <- gsub("'", "''", subjects)
    summaries <- gsub("'", "''", summaries)
    
    insert_query <- sprintf(
      "INSERT INTO datascience_dev.trending_topics.ai_summary (day_, subject, summary, summary_id) 
       VALUES ('%s', '%s', '%s', '%s')",
      temp_day, subjects, summaries, summary_id
    )
    
    for(j in insert_query){
    submitSnowflake(j, creds = snowflake_credentials)
    }
    
  }
  
```

SUMMARIZED: `r Sys.time()`

# Done 

You may now query `trending_topics.ai_summary`.
